---
title: "SBA Figure"
author: "Paul Testa and Jake Bowers"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r init,echo=F}
## Easy way to look for and install missing packages and load them
if (!require("pacman")){ install.packages("pacman") }
pacman::p_load("knitr","ggplot2","grid","gridExtra")

opts_chunk$set(tidy=TRUE,echo=TRUE,results='markup',strip.white=TRUE,cache=T,highlight=TRUE,width.cutoff=132,size='footnotesize',message=FALSE,warning=TRUE,comment=NA)

options(width=110,digits=4)
```

Document to create time series trend in SBA data

```{r data}
# Load sba.cvs (saved locally) containing monthly estimates
sba<-read.csv("sba.csv",as.is=TRUE,strip.white=TRUE)
```

```{r recodes}
# Rename date varialbe
print(sba$Date.Range)
sba$Date.Range[sba$Date.Range=="May 24 2016 - July 24 2015"]<-"May 24 2015 - July 24 2015"
sba$Date<-1:nrow(sba)

sba$Dates<-gsub("[[:blank:]]*- [[:alnum:]]*[[:blank:]]*[[:alnum:]]*[[:blank:]]*[[:alnum:]]*[[:alnum:]]*[[:alnum:]]","",sba$Date.Range)
sba$Dates<-gsub("Sept","Sep",sba$Dates)
#sba$Dates<-factor(sba$Dates,levels=sba$Dates)
library(lubridate)
sba$DateStart<-mdy(as.character(sba$Dates))

tmp<-(1-sba[,4]/sba[,3])*100
cbind(tmp,sba$Converstion.Rate.to.Course)
names(sba)[5]<-"ConversionRate"
sba$ConversionRate<-(1-sba[,4]/sba[,3])*100
class(sba[,"ConversionRate"])
sba$BeganCourse1000<-sba[,3]/1000

## Provided some information
names(sba)[names(sba)=="X..Completed.Some.Information"]<-"CompletedSomeInfo"
sba$SomeInfo<-with(sba,(Completed.Some.Information+Completed.All.Information)/(sba$Completed.Some.Information+sba$Completed.No.Information+sba$Completed.All.Information))*100

as.character(sba$Variation[1])
## sba$Form<-ifelse(sba$Variation=="Old Form","Pre Change","Post Change")
sba$Form<-ifelse(sba$Variation!="Old Form","New Form",as.character(sba$Variation))
```

Collapse the information about the new forms.

```{r,cache=F}

newdat <- sba[,c("Date","Dates","ConversionRate","SomeInfo","Form")]

newdat[newdat$Dates %in% c("Mar 25 2016","Apr 21 2016","May 24 2016"),"Dates"]<-"Mar 24 to May 24 2016"

newdat$ConversionRate[newdat$Dates=="Mar 24 to May 24 2016"]<-mean(newdat$ConversionRate[newdat$Dates=="Mar 24 to May 24 2016"])

newdat$SomeInfo[newdat$Dates=="Mar 24 to May 24 2016"]<-mean(newdat$SomeInfo[newdat$Dates=="Mar 24 to May 24 2016"])

newdat<-newdat[1:16,]
newdat$Dates<-factor(newdat$Dates,levels=newdat$Dates)
```


```{r figConversion,cache=F}
p_sba_conv<-ggplot(newdat,aes(x=Date,y=ConversionRate,col=Form))+geom_line()+geom_point()+
    scale_x_continuous(breaks=1:16,labels=newdat$Dates)+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs(y="Conversion Rate (%)",x="",title="Conversion Rate")
p_sba_conv
```


```{r figSomeInfo,cache=F}
p_sba_info<-ggplot(newdat,aes(x=Date,y=SomeInfo,col=Form))+geom_line()+geom_point()+
    scale_x_continuous(breaks=1:16,labels=newdat$Dates)+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs(y="Provided Some Information (%)",x="",title="Information Provision")
p_sba_info
```



```{r figPart,cache=F}
p_sba_part<-ggplot(sba,aes(x=Dates,y=BeganCourse1000,fill=Form))+geom_bar(stat="identity")+
   theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs(y="# (in Thousands)",x="Date",title="# Beginning Course")
p_sba_part
```

```{r}
# Slight edits to combine into one figure
p_sba_conv_c<-ggplot(sba,aes(x=Date,y=ConversionRate,col=Form))+geom_line()+
    scale_x_continuous(breaks=1:18,labels=sba$Dates)+ theme(axis.ticks = element_blank(), axis.text.x = element_blank())+labs(y="Conversion Rate (%)",x="",title="Conversion Rate")

p_sba_part_c<-ggplot(sba,aes(x=Dates,y=BeganCourse1000,fill=Form))+geom_bar(stat="identity")+
   theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs(y="# (in Thousands)",x="Date",title="# Beginning Course")


```


```{r figComb,fig.width=12}
grid.arrange(p_sba_conv,p_sba_info,ncol=2)
```


# Test of Proprotions: Conversion Rate

Do a test of proportions (prop.test) converting during mar--may 2016 versus average of jan and feb 2016. Also test mar--may 2016 versus mar--may 2015.
```{r conversionrates}
# Number converted
sba$Converted<-sba[,3]-sba[,4]
# Create table for prop test
contab1<-matrix(NA,2,2)
rownames(contab1)<-c("Mar-May 2016","Jan-Feb 2016")
colnames(contab1)<-c("Converted","Not Converted")
# Add success and failures
# Post change
contab1[1,]<-colSums(sba[sba$Dates%in%c("Mar 25 2016", "Apr 21 2016", "May 24 2016"),c(16,4)])
# January to Febuary
contab1[2,]<-colSums(sba[sba$Dates%in%c("Dec 25 2015", "Jan 25 2016","Feb 25 2016"),c(16,4)])
conprop1<-prop.test(contab1)
conprop1


# 
contab2<-matrix(NA,2,2)
rownames(contab2)<-c("Mar-May 2016","Mar-May 2015")
colnames(contab2)<-c("Converted","Not Converted")
# Add success and failures

contab2[1,]<-colSums(sba[sba$Dates%in%c("Mar 25 2016", "Apr 21 2016", "May 24 2016"),c(16,4)])
contab2[2,]<-colSums(sba[sba$Dates%in%c("Mar 25 2015", "Apr 21 2015", "May 24 2015"),c(16,4)])

conprop2<-prop.test(contab2)
conprop2




```

Compared to the proportion converting between January and February in 2016 (`r round(conprop1$estimate[2]*100,2)` percent), the new forms increased conversion by  `r round(diff(conprop1$estimate[c(2,1)])*100,2)` percent (p<0.001, 95% CI [`r round(conprop1$conf.int[1]*100,2)`, `r round(conprop1$conf.int[2]*100,2)`
])

Compared to the proportion converting between then end of March and May in 2016 (`r round(conprop2$estimate[2]*100,2)` percent), the new forms increased conversion by  `r round(diff(conprop2$estimate[c(2,1)])*100,2)` percent (p<0.001, 95% CI [`r round(conprop2$conf.int[1]*100,2)`, `r round(conprop2$conf.int[2]*100,2)`
])

# Test of Proportions: Some Information


```{r informationrates}
# Number converted
sba$SomeInfo_cnt<-sba$SomeInfo<-with(sba,Completed.Some.Information+Completed.All.Information)
sba$NoInfo_cnt<-sba$Completed.No.Information

# Create table for prop test
infotab1<-matrix(NA,2,2)
rownames(infotab1)<-c("Mar-May 2016","Dec 2015-Feb 2016")
colnames(infotab1)<-c("Some Info","No Info")
# Add success and failures
# Post change
infotab1[1,]<-colSums(sba[sba$Dates%in%c("Mar 25 2016", "Apr 21 2016", "May 24 2016"),c("SomeInfo_cnt","NoInfo_cnt")])
# January to Febuary
infotab1[2,]<-colSums(sba[sba$Dates%in%c("Dec 25 2015", "Jan 25 2016","Feb 25 2016"),c("SomeInfo_cnt","NoInfo_cnt")])
infoprop1<-prop.test(infotab1)
infoprop1


# 
infotab2<-matrix(NA,2,2)
rownames(infotab2)<-c("Mar-May 2016","Mar-May 2015")
colnames(infotab2)<-c("Converted","Not Converted")
# Add success and failures

infotab2[1,]<-colSums(sba[sba$Dates%in%c("Mar 25 2016", "Apr 21 2016", "May 24 2016"),c("SomeInfo_cnt","NoInfo_cnt")])
infotab2[2,]<-colSums(sba[sba$Dates%in%c("Mar 25 2015", "Apr 21 2015", "May 24 2015"),c("SomeInfo_cnt","NoInfo_cnt")],na.rm=T)

infoprop2<-prop.test(infotab2)
infoprop2




```

Compared to the proportion providing some info between January and February in 2016 (`r round(infoprop1$estimate[2]*100,2)` percent), the new forms increased information provision by  `r round(diff(infoprop1$estimate[c(2,1)])*100,2)` percent (p<0.001, 95% CI [`r round(infoprop1$conf.int[1]*100,2)`, `r round(infoprop1$conf.int[2]*100,2)`
])

Compared to the proportion converting between then end of March and May in 2016 (`r round(infoprop2$estimate[2]*100,2)` percent), the new forms increased information provision by  `r round(diff(infoprop2$estimate[c(2,1)])*100,2)` percent (p<0.001, 95% CI [`r round(infoprop2$conf.int[1]*100,2)`, `r round(infoprop2$conf.int[2]*100,2)`
])
